Canadian Discrimination Analysis with GSS (2014)

### 2022-03-22 outputs/paper/paper.Rmd
intro change

The remainder sections would show that it is worth paying attention to the discrimination problem in Canada. Section \@ref(data) would introduce our data. Section \@ref(results) would present our results about certain discrimination concerns evaluated based on our data. Section \@ref(discussion) would illustrate our explanation and discussions regarding our results. Section \@ref(appendix) includes a more detailed demonstration mentioned in the previous sections with a supplementary survey created for our analysis. Section \@ref(reference) includes our references for this paper.

@@

```{r sex-crime-plot, fig.height=4, fig.cap="Sex Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
sex_crime_plot
```

```{r culture-crime-plot, fig.height=4, fig.cap="Ethnicity or culture Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
culture_crime_plot
```

```{r race-skin-crime-plot, fig.height=4, fig.cap="Race and Skin Color Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
race_skin_crime_plot
```

```{r physical-appearance-crime-plot, fig.height=4, fig.cap="Physical appearance Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_appearance_crime_plot
```

```{r religion-crime-plot, fig.height=4, fig.cap="Religion Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
religion_crime_plot
```

```{r sexual-orientation-crime-plot, fig.height=4, fig.cap="Sexual orientation Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
sexual_orientation_crime_plot
```

```{r age-crime-plot, fig.height=4, fig.cap="Age Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
age_crime_plot
```

```{r physical-mental-disability-crime-plot, fig.height=4, fig.cap="Physical or mental disability Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
physical_mental_disability_crime_plot
```

```{r language-crime-plot, fig.height=4, fig.cap="Language Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE}
language_crime_plot
```

```{r university-education-vs-crime, fig.cap="University Education VS Crime", fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01c < 3),
                            col1 = "eor_01c", col2 = "msvic",
                      col1_num=eor_01c_num, col1_labels=eor_01c_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="University Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime",
                      plot_ylab="Percentage", 
                      plot_fill_lab="Education")
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s1.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s2.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s3.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s4.jpg"))
```

```{r, out.width='800px', echo=F}
knitr::include_graphics(here::here("outputs/paper/s5.jpg"))
```

>>>>

The remainder sections would show that it is worth paying attention to the discrimination problem in Canada. Section \@ref(data) would introduce our data. Section \@ref(results) would present our results about certain discrimination concerns evaluated based on our data. Section \@ref(discussion) would illustrate our explanation and discussions regarding our results. Section \@ref(appendix) includes a more detailed demonstration mentioned in the previous sections with a supplementary survey created for our analysis. The last section includes our references for this paper.

@@

```{r sex-crime-plot, fig.height=4, fig.cap="Sex Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
sex_crime_plot
```

```{r culture-crime-plot, fig.height=4, fig.cap="Ethnicity or culture Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
culture_crime_plot
```

```{r race-skin-crime-plot, fig.height=4, fig.cap="Race and Skin Color Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
race_skin_crime_plot
```

```{r physical-appearance-crime-plot, fig.height=4, fig.cap="Physical appearance Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
physical_appearance_crime_plot
```

```{r religion-crime-plot, fig.height=4, fig.cap="Religion Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
religion_crime_plot
```

```{r sexual-orientation-crime-plot, fig.height=4, fig.cap="Sexual orientation Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
sexual_orientation_crime_plot
```

```{r age-crime-plot, fig.height=4, fig.cap="Age Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
age_crime_plot
```

```{r physical-mental-disability-crime-plot, fig.height=4, fig.cap="Physical or mental disability Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
physical_mental_disability_crime_plot
```

```{r language-crime-plot, fig.height=4, fig.cap="Language Discrimination VS Crime", echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
language_crime_plot
```

```{r university-education-vs-crime, fig.cap="University Education VS Crime", fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE, fig.pos = "!H"}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01c < 3),
                            col1 = "eor_01c", col2 = "msvic",
                      col1_num=eor_01c_num, col1_labels=eor_01c_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="University Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime",
                      plot_ylab="Percentage", 
                      plot_fill_lab="Education")
```

```{r, out.width='800px', echo=F, fig.pos = "!H"}
knitr::include_graphics(here::here("outputs/paper/s.jpg"))
```

```{r, out.width='800px', echo=F, fig.pos = "!H"}
knitr::include_graphics(here::here("outputs/paper/s1.jpg"))
```

```{r, out.width='800px', echo=F, fig.pos = "!H"}
knitr::include_graphics(here::here("outputs/paper/s2.jpg"))
```

```{r, out.width='800px', echo=F, fig.pos = "!H"}
knitr::include_graphics(here::here("outputs/paper/s3.jpg"))
```

```{r, out.width='800px', echo=F, fig.pos = "!H"}
knitr::include_graphics(here::here("outputs/paper/s4.jpg"))
```

```{r, out.width='800px', echo=F, fig.pos = "!H"}
knitr::include_graphics(here::here("outputs/paper/s5.jpg"))
```
